Abstract Data Type Inference

### 2015-03-13 algorithm.tex
Fixed typo.
Fixed a couple of definitions.

A \emph{well-quasi-ordering (wqo)} $R$ on a set $X$ is a reflexive, transitive
binary relation on $X$ for which in every infinite sequence $x_0 x_1 \ldots$ of
elements from $X$, there exists a pair $x_i, x_j$, for $i \neq j$, related by
$R$.

@@

  $\preceq$ is a wqo on width-$k$ histories, for any $k \in \mathbb{N}$.

@@

Computing $B$ thus amounts to computing its finite representation. In general,
this is achieved by enumerating the elements of $B$ while maintaining the
$\preceq$-minimal elements, and recognizing a condition under which all
elements of $B$ are related to the current set of
minimals~\cite{conf/lics/AbdullaCJT96, journals/tcs/FinkelS01}. In our case, we
recognize a condition on the weight-increasing enumeration of $B$ which
guarantees coverage by the current set of minimals. Formally, for all $i \in
\mathbb{N}$, we define
\begin{align*}
  B_i &= \set{ h \in B : \weight(h) \le i } \\
  B_i' &= \set{ h' \in B :
    \exists h \in B_i.\ h \preceq h' \text{ and } \weight(h) \le i+1
  }
\end{align*}
as, respectively, the histories of $B$ with at most $i$ matches and duplicates,
and those derived from $B_i$ with at most $i\!+\!1$ matches and duplicates. We
say that $A$ is \emph{predictable} if $B_i = B$ whenever $B_i' = B_{i+1}$. In
Section~\ref{sec:nature} we demonstrate that naturally-occurring ADTs are
predictable. Since the number of weight-$i$ histories is finite\footnote{As
noted in Section~\ref{sec:histories}, we consider equality between histories up
to renaming of operation identifiers.} for each $i \in \mathbb{N}$, each $B_i$
is computable.

>>>>

A \emph{well-quasi-ordering (wqo)} $R$ on a set $X$ is a reflexive, transitive
binary relation on $X$ for which in every infinite sequence $x_0 x_1 \ldots$ of
elements from $X$, there exists indices $i < j$ such that $R(x_i,x_j)$.

@@

  $\preceq$ is a wqo on width-bounded histories.

@@

Computing $B$ thus amounts to computing its finite representation. In general,
this is achieved by enumerating the elements of $B$ while maintaining the
$\preceq$-minimal elements, and recognizing a condition under which all
elements of $B$ are related to the current set of
minimals~\cite{conf/lics/AbdullaCJT96, journals/tcs/FinkelS01}. In our case, we
recognize a condition on the weight-increasing enumeration of $B$ which
guarantees coverage by the current set of minimals. Formally, for all $i \in
\mathbb{N}$, we define
\begin{align*}
  B_i &= \set{ h \in B : \weight(h) \le i } \\
  B_i' &= \set{ h' \in B :
    \exists h \in B_i.\ h \preceq h' \text{ and } \weight(h') \le i+1
  }
\end{align*}
as, respectively, the histories of $B$ with at most $i$ matches and duplicates,
and those derived from $B_i$ with at most $i\!+\!1$ matches and duplicates. We
say that $A$ is \emph{predictable} if $B_i = B$ whenever $B_i' = B_{i+1}$. In
Section~\ref{sec:nature} we demonstrate that naturally-occurring ADTs are
predictable. Since the number of weight-$i$ histories is finite\footnote{As
noted in Section~\ref{sec:histories}, we consider equality between histories up
to renaming of operation identifiers.} for each $i \in \mathbb{N}$, each $B_i$
is computable.

### 2015-03-13 histories.tex
Fixed a couple of definitions.

\end{itemize}
Non-completed operations are \emph{pending}, and are maximal in the
happens-before order. The \emph{width} of a history is the maximum number of
its operations which are mutually unordered, and the \emph{width} of a history
set is the maximum width of its elements. Width-$1$ histories are
\emph{sequential}. An operation $o \in \rng(m)$ is a \emph{match target}, and
the set $\set{ o' \in O : m(o') = o}$ of operations targeting $o$ is a
\emph{match}. We assume targets target themselves: $m(o) = o$ for $o \in
\rng(m)$. The \emph{weight} of $h$ is the number $|\rng(m)|$ of matches.
Since the operation identifiers of a history have no intrinsic meaning, we
consider equality between histories up to renaming of operation identifiers.

>>>>

\end{itemize}
Non-completed operations are \emph{pending}, and are maximal in the
happens-before order. The \emph{width} of a history is the maximum number of
its operations which are mutually unordered, and the \emph{width} of a history
set is the maximum width of its elements. Width-$1$ histories are
\emph{sequential}.
Two operations $o, o'$ are \emph{identical}, written $o \sim o'$, when they
have the same labels: $c(o) = c(o')$, $f(o) = f(o')$, and matching: $m(o) =
m(o')$. The \emph{frequency} of an operation $o$ is the number $\freq(o) =
|\set{ o' \in O : o \sim o' }|$ of operations identical to $o$, and $o$ has
\emph{duplicates} when $\freq(o) > 1$. An operation $o \in \rng(m)$ is a
\emph{match target}, and the set $\set{ o' \in O : m(o') = o}$ of operations
targeting $o$ is a \emph{match}. We assume targets target themselves: $m(o) =
o$ for $o \in \rng(m)$. The \emph{weight} of $h$ is the maximum $\max(\set{
\freq(o) : o \in O } \cup \set{|\rng(m)|})$ between operation frequencies and
the number of matches. Since the operation identifiers of a history have no
intrinsic meaning, we consider equality between histories up to renaming of
operation identifiers.
